Appendix

### 2025-04-04 manuscript_rmarkdown/manuscript_appendix.Rmd
Rework optimisation of weighting parameters to use a combined loss
Prevents myopic focus on reducing residuals.

data <- .assess_standardisation_before_transformation_simulation(lambda_limit = c(-4.0, 6.0))
data <- data[, mget(c("residuals", "lambda", "p_value", "transformation", "dataset"))]
data[, "residuals" := round(residuals, digits = 1L)]
data[, "lambda" := round(lambda, digits = 1L)]
data[, "p_value" := round(p_value, digits = 3L)]
data.table::dcast(data, transformation ~ dataset, value.var = "residuals")
data.table::dcast(data, transformation ~ dataset, value.var = "lambda")
data.table::dcast(data, transformation ~ dataset, value.var = "p_value")
```

@@

# Yeo-Johnson on clean and dirty data.
clean_data <- .assess_simulated_data(manuscript_dir = manuscript_dir, data_type = "clean", method = "box_cox")
dirty_data <- .assess_simulated_data(manuscript_dir = manuscript_dir, data_type = "dirty", method = "box_cox")
shifted_data <- .assess_simulated_data(manuscript_dir = manuscript_dir, data_type = "dirty_shifted", method = "box_cox")

@@

# Add rank based on residual error for central normality.
data[, "method_rank" := rank(residuals), by = c("experiment_id", "outlier", "dataset")]

@@

>>>>

data <- .assess_standardisation_before_transformation_simulation(lambda_limit = c(-4.0, 6.0))
data <- data[, mget(c("residuals", "residuals_central", "lambda", "p_value", "transformation", "dataset"))]
data[, "residuals" := round(residuals, digits = 1L)]
data[, "residuals_central" := round(residuals_central, digits = 1L)]
data[, "lambda" := round(lambda, digits = 1L)]
data[, "p_value" := round(p_value, digits = 3L)]
data.table::dcast(data, transformation ~ dataset, value.var = "residuals")
data.table::dcast(data, transformation ~ dataset, value.var = "residuals_central")
data.table::dcast(data, transformation ~ dataset, value.var = "lambda")
data.table::dcast(data, transformation ~ dataset, value.var = "p_value")
```

@@

# Box-Cox on clean and dirty data.
clean_data <- .assess_simulated_data(manuscript_dir = manuscript_dir, data_type = "clean", method = "box_cox")
dirty_data <- .assess_simulated_data(manuscript_dir = manuscript_dir, data_type = "dirty", method = "box_cox")
shifted_data <- .assess_simulated_data(manuscript_dir = manuscript_dir, data_type = "dirty_shifted", method = "box_cox")

@@

# Add rank based on residual error for central normality.
data[outlier == FALSE, "method_rank" := rank(residuals), by = c("experiment_id", "outlier", "dataset")]
data[outlier == TRUE, "method_rank" := rank(residuals_central), by = c("experiment_id", "outlier", "dataset")]

@@

data <- .assess_standardisation_before_transformation_simulation(lambda_limit = c(-4.0, 6.0), method = "box_cox")
data <- data[, mget(c("residuals", "residuals_central", "lambda", "p_value", "transformation", "dataset"))]
data[, "residuals" := round(residuals, digits = 1L)]
data[, "residuals_central" := round(residuals, digits = 1L)]
data[, "lambda" := round(lambda, digits = 1L)]
data[, "p_value" := round(p_value, digits = 3L)]
data.table::dcast(data, transformation ~ dataset, value.var = "residuals")
data.table::dcast(data, transformation ~ dataset, value.var = "residuals_central")
data.table::dcast(data, transformation ~ dataset, value.var = "lambda")
data.table::dcast(data, transformation ~ dataset, value.var = "p_value")
```
